\section{Evaluation}
\label{sec.eval}
Our objective with this project was to \emph{explore if it is possible to abstract the creation of simple location-based systems from a programming level to a configuration level} and to \emph{discuss to what extent our system can support complex interactions between user and system}. To evaluate to what extend we have met this objective, we will conducted an evaluation in three parts. First we evaluated the Realms configurator with users by having them configure a realm. Second, we evaluated the mobile client with users having to explore some predefined realms. Third and last, we will discussed our system and compare it to existing apps. In this section we present the evaluation setup and the results. In the next section we will discuss the results.

\subsection{Configuration Manager Evaluation} % (fold)
\label{sub:configuration_manager_evaluation}
We will evaluate the configuration manager with users - preferably with knowledge of app but not necessarily with programming experience. The evaluation should focus on usefulness and usability

For the test we created a scenario where users are asked to take on the position as a employee in the Copenhagen municipality. 
% subsection configuration_manager_evaluation (end)

\subsection{Android Application Evaluation} % (fold)
\label{sub:android_application_evaluation}
While the main focus for realms is the creation of realms through the configuration manager, we should still evaluate the Android application for accessing realms. We evaluated the client app by creating a configuration and had users explore that realm.

We created a realm with the purpose of rating architecture around the city. The realm covered the IT University of Copenhagen as well as the surrounding building that include Copenhagen University buildings, an office building, a library, several apartment building and a some student housings. For each of these buildings we created a  mark with a description of the building, the year it was raised and the name of the architect who designed it. Our test users were given the task to go outside, enter the "Architecture Amager" realm, and walk around to different buildings in the area to explore the marks and rate them.  

(Insert screenshot of configuration here)
% subsection android_application_evaluation (end)